Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber}}

### 2018-03-26 Paper.tex
Add bitwise shifting instructions EIP-145
https://github.com/ethereum/EIPs/blob/f6a0ec6c37b878b8f063b54a44c60013007f5b99/EIPS/eip-145.md

\multicolumn{5}{l}{$\boldsymbol{\mu}_{\mathbf{s}}[x]_{\mathrm{i}}$ gives the $i$th bit (counting from zero) of $\boldsymbol{\mu}_{\mathbf{s}}[x]$} \vspace{5pt} \\

>>>>

& \multicolumn{4}{l}{$\boldsymbol{\mu}_{\mathbf{s}}[x]_{\mathrm{i}}$ gives the $i$th bit (counting from zero) of $\boldsymbol{\mu}_{\mathbf{s}}[x]$} \vspace{5pt}  \\
0x1b & {\small SHL} & 2 & 1 & Bitwise shifting to the left. \\
&&&& $\boldsymbol{\mu}'_{\mathbf{s}}[0] \equiv 2 ^ {\boldsymbol{\mu}_{\mathbf{s}}[0]} \times \boldsymbol{\mu}_{\mathbf{s}}[1].$ \\
0x1c & {\small SHR} & 2 & 1 & Bitwise logical shifting to the right. \\
&&&& $\boldsymbol{\mu}'_{\mathbf{s}}[0] \equiv \left\lfloor \dfrac{ \boldsymbol{\mu}_{\mathbf{s}}[1]}{ 2 ^ {\boldsymbol{\mu}_{\mathbf{s}}[0]} } \right\rfloor$
\\
0x1d & {\small SAR} & 2 & 1 & Bitwise arithmetic shifting to the right. \\
&&&& $\boldsymbol{\mu}'_{\mathbf{s}}[0] \equiv \left\lfloor \dfrac{ \boldsymbol{\mu}_{\mathbf{s}}[1]}{ 2 ^ {\boldsymbol{\mu}_{\mathbf{s}}[0]} } \right\rfloor$ \\
& \multicolumn{4}{l}{where $\boldsymbol{\mu}_{\mathbf{s}}[1]$ is treated as two's complement signed 256-bit integer.}  \\
